Introduction

### 2015-07-19 dissertation/problems.tex
new header
First problem def

\subsection{Performance problems}

\subsection{Stability problems}

\subsection{Problems with evaluations}

\subsection{Development problems}

>>>>

\subsection{Performance problems}\label{sec:perfproblems}

\subsection{Stability problems}\label{sec:stabproblems}

\subsection{Problems of shared understanding}\label{sec:semproblems}

\subsection{Problems with evaluations}\label{sec:evalproblems}

\subsection{Development problems}\label{sec:devproblems}

There are several issues that make Semantic Web development difficult,
that are connected with development in current programming languages
and current Semantic Web libraries. As pointed out in \cite{darobin1},
there are few things that are simpler in contemporary programming than
to parse a string containing a tree-formatted data structure into a
tree that can be accessed directly. However, RDF makes the assumption
that the natural form of data is not a tree, but a graph, and in the
general case, it must be addressed as such.

\begin{problem}\label{prob:graph}
Addressing graph data in a programming language.
\end{problem}
